---
title: "STAT515_005 FINAL PROJECT GROUP 7 - CREDIT CARD FRAUD DETECTION"
author: "Vedant Shamling Limbhare, Prathyusha Elipay"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(geosphere)
library(caTools)
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(ROSE)
library(ROCR)
library(pROC)
library(tree)
library(sparkline)
library(visNetwork)
library(Rborist)
library(xgboost)
```

```{r, message=FALSE}
cc_fraud_original <- as.data.frame(read_csv("credit_card_fraud.csv"))
str(cc_fraud_original)
```

```{r}
any(is.na(cc_fraud_original))
```

```{r}

cities <- c("Albuquerque", "American Fork", "Arvada", "Aurora", "Azusa", "Ballwin", "Bay City", "Broomfield", "Burbank",
            "Burlington", "Camden", "Campbell", "Caroll", "Colorado Springs", "Colton", "Conway", "Corona", "Daly City", "Downey",
            "Espanola", "Eugene", "Fullerton", "Glendale", "Huntington Beach", "Independence", "Issaquah", "Kansas City", "Kent",
            "Kirk", "Kirtland Afb", "La Grande", "Laguna Hills", "Lake Oswego", "Laramie", "Littleton", "Los Angeles", "Lowell",
            "Malad City", "Manville", "Matthews", "Meadville", "Meridian", "Mesa", "Moab", "Moriarty", "Napa", "Newberg", "Newhall",
            "Norwalk", "Oakland", "Odessa", "Omaha", "Owensville", "Palmdale", "Parker", "Parker Dam", "Phoenix", "Pleasant Hill",
            "Portland", "Pueblo", "Ravenna", "Red Cliff", "Red River", "Redford", "Riverton", "Rock Springs", "Rocky Mount",
            "Roseland", "Ruidoso", "Sacramento", "Saint Louis", "San Diego", "San Jose", "Santa Monica", "Scotts Mills", "Seattle",
            "Seligman", "Shedd", "Smith River", "Spirit Lake", "Stayton", "Sun City", "Syracuse", "Tekoa", "Thompson", "Unionville",
            "Utica", "Vancouver", "Vinton", "Westerville", "Westfir", "Wheaton", "Williamsburg", "Woods Cross")

business_jobs <- c("Accountant", "Advertising account planner", "Airline pilot", "Associate Professor", "Buyer, industrial", 
                   "Call centre manager", "Chief Marketing Officer", "Comptroller", "Contractor", "Economist", 
                   "Education administrator", "Education officer, museum", "Engineering managers", "Freight forwarder", 
                   "Hotel manager", "Human resources officer", "Information systems manager", "Insurance broker", 
                   "Investment analyst", "Investment banker, corporate", "IT consultant", "Lecturer, higher education", 
                   "Local government officer", "Marketing executive", "Occupational hygienist", 
                   "Product/process development scientist", "Production manager", "Public house manager", 
                   "Public relations account executive", "Retail merchandiser", "Sales executive, IT", "Surveyor, minerals", 
                   "Systems analyst", "Tax inspector", "Tourist information centre manager")


engineering_jobs <- c("Aeronautical engineer", "Agricultural consultant", "Architect", "Architectural technologist", 
                      "Armed forces training and education officer", "Building surveyor", "Chemical engineer", 
                      "Civil engineer, contracting", "Civil Service administrator", "Civil Service fast streamer", 
                      "Colour technologist", "Development worker, international aid", "Electronics engineer", "Engineer, automotive", 
                      "Engineer, biomedical", "Engineer, building services", "Engineer, civil (consulting)", 
                      "Engineer, communications", "Engineer, electronics", "Engineer, maintenance", "Engineer, petroleum", 
                      "Engineer, production", "Engineer, site", "Geologist, engineering", "Geoscientist", "Materials engineer", 
                      "Metallurgist", "Naval architect", "Network engineer", "Petroleum engineer", 
                      "Planning and development surveyor", "Product designer", "Research scientist (physical sciences)", 
                      "Scientist, marine", "Scientist, physiological", "Surveyor, land/geomatics", "Surveyor, mining", 
                      "Systems developer", "Water engineer", "Wellsite geologist")


healthcare_jobs <- c("Chiropodist", "Clinical cytogeneticist", "Clinical research associate", "Counselling psychologist", 
                     "Counsellor", "Cytogeneticist", "Exercise physiologist", "Fine artist", "Forensic psychologist", 
                     "Health physicist", "Health service manager", "Mental health nurse", "Music therapist", "Nurse, children's", 
                     "Nurse, mental health", "Occupational psychologist", "Osteopath", "Pharmacist, hospital", "Physiotherapist", 
                     "Scientist, audiological", "Scientist, research (maths)", "Therapist, art", "Therapist, horticultural", 
                     "Therapist, music", "Therapist, occupational")

creative_jobs <- c("Glass blower/designer", "Historic buildings inspector/conservation officer", "Journalist, newspaper", 
                   "Landscape architect", "Location manager", "Magazine features editor", "Museum education officer", 
                   "Museum/gallery exhibitions officer", "Musician", "Set designer", "Television/film/video producer", "Video editor")

legal_jobs <- c("Barrister", "Careers information officer", "Chartered legal executive (England and Wales)", 
                "Chartered public finance accountant", "Community arts worker", "Immigration officer", "Intelligence analyst", 
                "Licensed conveyancer", "Public librarian", "Research officer, political party", "Solicitor, Scotland", 
                "Special educational needs teacher")

education_jobs <- c("Early years teacher", "Learning mentor", "Private music teacher", "Teacher, adult education", 
                    "Teacher, early years/pre", "Teaching laboratory technician", "TEFL teacher")
```

```{r}
cc_fraud <- cc_fraud_original %>%
  reframe(area = ifelse(cc_fraud_original$state %in% c("AK", "CA", "HI", "OR", "WA"), "west",
                        ifelse(cc_fraud_original$state %in% c("MO", "NE"), "midwest", "southwest")),
          city_type = ifelse(cc_fraud_original$city %in% cities, "urban", "rural"),
          city_pop = city_pop,
          merchant_type = ifelse(cc_fraud_original$category %in% 
                                   c("gas_transport", "grocery_net", "grocery_pos", "health_fitness", "home", "kids_pets",
                                     "personal_care"), "essential", "discretionary"),
          trans_amt = round(amt, 2),
          trans_hour = ifelse(format(trans_date_trans_time, "%H") %in% c(6:11), "morning", 
                              ifelse(format(trans_date_trans_time, "%H") %in% c(12:18), "afternoon",
                                     ifelse(format(trans_date_trans_time, "%H") %in% c(17:22), "evening", "night"))), 
          is_weekend = ifelse(format(cc_fraud_original$trans_date_trans_time, "%A") %in% c("Saturday", "Sunday"), 1, 0),
          cc_holder_age = as.numeric(round(difftime(cc_fraud_original$trans_date_trans_time, cc_fraud_original$dob, 
                                          units = "days") / 365.25, 0)),
          is_business_jobs = ifelse(cc_fraud_original$job %in% business_jobs, "1", "0"),
          is_engineering_jobs = ifelse(cc_fraud_original$job %in% engineering_jobs, "1", "0"),
          is_healthcare_jobs = ifelse(cc_fraud_original$job %in% healthcare_jobs, "1", "0"),
          is_creative_jobs = ifelse(cc_fraud_original$job %in% creative_jobs, "1", "0"),
          is_legal_jobs = ifelse(cc_fraud_original$job %in% legal_jobs, "1", "0"),
          is_education_jobs = ifelse(cc_fraud_original$job %in% education_jobs, "1", "0"),
          is_fraud = is_fraud)
```

```{r}
for(i in 1:nrow(cc_fraud_original)){
  cc_fraud$dist_merch_trans[i] = round(distm(x = c(cc_fraud_original$long[i], cc_fraud_original$lat[i]), 
                                             y = c(cc_fraud_original$merch_long[i], cc_fraud_original$merch_lat[i]), 
                                             fun = distGeo)/1609.34, 2)
}
```

```{r}
cat("range of distances: ", range(cc_fraud$dist_merch_trans))
cat("\nmean distance: ", mean(cc_fraud$dist_merch_trans))
cat("\nmedian distance: ", median(cc_fraud$dist_merch_trans))

min_dist <- min(cc_fraud$dist_merch_trans)
max_dist <- max(cc_fraud$dist_merch_trans)
interval <- (max_dist - min_dist) / 3

distance_meter <- c(min_dist + interval, min_dist + 2*interval)
distance_meter
```

```{r}
cc_fraud <- mutate(cc_fraud, area = as.factor(area),
                   city_type = as.factor(city_type),
                   merchant_type = as.factor(merchant_type),
                   trans_hour = as.factor(trans_hour),
                   is_weekend = as.factor(is_weekend),
                   is_business_jobs = as.factor(is_business_jobs),
                   is_engineering_jobs = as.factor(is_engineering_jobs),
                   is_healthcare_jobs = as.factor(is_healthcare_jobs),
                   is_creative_jobs = as.factor(is_creative_jobs),
                   is_legal_jobs = as.factor(is_legal_jobs),
                   is_education_jobs = as.factor(is_education_jobs),
                   dist_merch_trans = ifelse(dist_merch_trans < distance_meter[1], "short_range", 
                                             if_else(dist_merch_trans > distance_meter[2], "long_range", "medium_range")),
                   dist_merch_trans = as.factor(dist_merch_trans),
                   is_fraud = as.factor(is_fraud)
)

str(cc_fraud)
```

```{r}
any(is.na(cc_fraud))
```

```{r}
summary(cc_fraud)
```

```{r}
range(cc_fraud$city_pop)

```

```{r eval=FALSE, include=FALSE}
breaks <- c(0, 1000, 10000, 100000, Inf)

cc_fraud$city_pop <- cut(cc_fraud$city_pop, breaks = breaks, labels = c("small", "medium", "large", "mega"))

table(cc_fraud$city_pop)

cc_fraud$city_pop = as.factor(cc_fraud$city_pop)
```

Predictive Modelling:

```{r}
set.seed(1)
split <- sample.split(cc_fraud$is_fraud, SplitRatio = 0.8)
train <- subset(cc_fraud, split == T)
cv <- subset(cc_fraud, split == F)

table(cv$is_fraud)

```

Decision tree model:

```{r}
tree.model <- rpart(is_fraud ~ ., data = train, method = "class", minbucket = 20)
visTree(tree.model)
```

```{r}
tree.predict <- predict(tree.model, cv, type = "class")
confusionMatrix(cv$is_fraud, tree.predict)
```

```{r}
tree.predict <- predict(tree.model, cv, type = "prob")
tree.ROCR <- prediction(tree.predict[,2], cv$is_fraud)
tree.predictions_1 <- tree.predict[,2]
tree.auc <- as.numeric(performance(tree.ROCR,"auc")@y.values)
tree.auc
```

Sampling using Decision Tree:
Over-Sampled

```{r}
oversampled_train_data <- ovun.sample(is_fraud ~ ., data = train, method = "over",
                                      N = 2*nrow(subset(train, train$is_fraud == 0)))$data
table(oversampled_train_data$is_fraud)
```

```{r}
tree.model.over <- rpart(is_fraud ~ ., data = oversampled_train_data, method = "class", minbucket = 20)
visTree(tree.model.over)
```

```{r}
tree.predict.over <- predict(tree.model.over, cv, type = "class")
confusionMatrix(cv$is_fraud, tree.predict.over)
```

```{r}
tree.predict.over <- predict(tree.model.over, cv, type = "prob")
tree.ROCR.over <- prediction(tree.predict.over[,2], cv$is_fraud )
tree.predictions_2 <- tree.predict.over[,2]
tree.auc.over <- as.numeric(performance(tree.ROCR.over,"auc")@y.values)
tree.auc.over
```

Under sampling:

```{r}
undersampled_train_data <- ovun.sample(is_fraud ~ ., data = train, method = "under",
                                      N = 2*nrow(subset(train, train$is_fraud == 1)), seed = 1)$data
table(undersampled_train_data$is_fraud)
```

```{r}
tree.model.under <- rpart(is_fraud ~ ., data = undersampled_train_data, method = "class", minbucket = 20)
visTree(tree.model.under)
```

```{r}
tree.predict.under <- predict(tree.model.under, cv, type = "class")
confusionMatrix(cv$is_fraud, tree.predict.under)
```

```{r}
tree.predict.under <- predict(tree.model.under, cv, type = "prob")
tree.ROCR.under <- prediction(tree.predict.under[,2], cv$is_fraud)
tree.predictions_3 <- tree.predict.under[,2]
tree.auc.under <- as.numeric(performance(tree.ROCR.under,"auc")@y.values)
tree.auc.under
```

Mix of both, over and under sampling:

```{r}
mix_sampled_train_data <- ovun.sample(is_fraud ~ ., data = train, method = "both", p=0.5, 
                                  N=nrow(train), seed = 1)$data
table(mix_sampled_train_data$is_fraud)
```

```{r}
tree.model.both <- rpart(is_fraud ~ ., data = mix_sampled_train_data, method = "class", minbucket = 20)
visTree(tree.model.both)
```

```{r}
tree.predict.both <- predict(tree.model.both, cv, type = "class")
confusionMatrix(cv$is_fraud, tree.predict.both)
```

```{r}
tree.predict.both <- predict(tree.model.both, cv, type = "prob")
tree.ROCR.both <- prediction(tree.predict.both[,2], cv$is_fraud)
tree.predictions_4 <- tree.predict.both[,2]
tree.auc.both <- as.numeric(performance(tree.ROCR.both,"auc")@y.values)
tree.auc.both
```

ROSE: Generation of synthetic data by –> Randomly Over Sampling Examples

```{r}
rose_train_data <- ROSE(is_fraud ~ ., data = train, seed = 1)$data
table(rose_train_data$is_fraud)
```

```{r}
tree.model.rose <- rpart(is_fraud ~ ., data = rose_train_data, method = "class", minbucket = 20)
visTree(tree.model)
```

```{r}
tree.predict.rose <- predict(tree.model.rose, cv, type = "class")
confusionMatrix(cv$is_fraud, tree.predict.rose)
```

```{r message=FALSE}
tree.predict.rose <- predict(tree.model.rose, cv, type = "prob")
tree.ROCR.rose <- prediction(tree.predict.rose[,2], cv$is_fraud)
tree.predictions_5 <- tree.predict.rose[,2]
tree.auc.rose <- as.numeric(performance(tree.ROCR.rose, "auc")@y.values)
tree.auc.rose

tree.ROCR.rose <- prediction(tree.predict.rose[, 2], cv$is_fraud)

auc <- roc(response = cv$is_fraud, predictor = tree.predict.rose[, 2])
auc
```

```{r}
result.auc <- data.frame(normal.auc = tree.auc, over.auc = tree.auc.over, under.auc = tree.auc.under, mix.auc = tree.auc.both, rose.auc = tree.auc.rose)
result.auc
```

ROC Plots for Decision Tree with Sampled Data:

```{r message=FALSE}
cv$trans_amt <- as.numeric(as.character(cv$trans_amt))
cv$cc_holder_age <- as.numeric(as.character(cv$cc_holder_age))

test_data_XG <- model.matrix(~.-1, data = cv)

test_x <- test_data_XG[, -19]
test_y <- test_data_XG[, 19]
model_labels <- c("Normal", "Over Sampling" ,"Under Sampling", "Mixed Sampling", "Rose Sampling")

plot(0, 0, xlim = c(0, 1), ylim = c(0, 1), type = "n", xlab = "False Positive Rate", ylab = "True Positive Rate", main = "ROC Curves - Different Sampling Methods in Decision Tree")

legend_labels <- c()
auc_values <- c()

for (i in 1:5) {
  pred_probs_model <- eval(parse(text = paste0("tree.predictions_", i)))
  roc_obj <- roc(test_y, pred_probs_model)
  lines(roc_obj, col = i)
  auc_values[i] <- auc(roc_obj)
  legend_labels <- c(legend_labels, paste(model_labels[i], "AUC =", round(auc_values[i], 4)))
}

abline(v = seq(0, 1, 0.1), h = seq(0, 1, 0.1), col = "lightgray", lty = "dotted")

legend("bottomleft", legend = legend_labels, col = 1:5, lwd = 1)

```


Random Forest:

```{r message=FALSE}
set.seed(10)
rf.model <- randomForest(is_fraud ~ ., data = train,
                         ntree = 500, nodesize = 20)

rf.predict <- predict(rf.model, cv)
rf_probs <- predict(rf.model, cv, type = "prob")[, 2]
rf_probs_1 <- predict(rf.model, cv, type = "prob")[, 2]
rf_auc <- auc(cv$is_fraud, rf_probs)
confusionMatrix(cv$is_fraud, rf.predict)
rf_auc
```


```{r}
varImpPlot(rf.model)
```

Over Sampled data RF:

```{r message=FALSE}
set.seed(10)
rf.model <- randomForest(is_fraud ~ ., data = oversampled_train_data,
                         ntree = 100, nodesize = 20)

rf.predict <- predict(rf.model, cv)
rf_probs <- predict(rf.model, cv, type = "prob")[, 2]
rf_probs_2 <- predict(rf.model, cv, type = "prob")[, 2]
rf_auc <- auc(cv$is_fraud, rf_probs)
confusionMatrix(cv$is_fraud, rf.predict)
rf_auc
```

Under Sampled data RF:

```{r}
set.seed(10)
rf.model <- randomForest(is_fraud ~ ., data = undersampled_train_data,
                         ntree = 500, nodesize = 20)

rf.predict <- predict(rf.model, cv)
rf_probs <- predict(rf.model, cv, type = "prob")[, 2]
rf_probs_3 <- predict(rf.model, cv, type = "prob")[, 2]
rf_auc <- auc(cv$is_fraud, rf_probs)
confusionMatrix(cv$is_fraud, rf.predict)
rf_auc
```

Mixed Sampled data RF:

```{r}
set.seed(10)
rf.model <- randomForest(is_fraud ~ ., data = mix_sampled_train_data,
                         ntree = 500, nodesize = 20)

rf.predict <- predict(rf.model, cv)
rf_probs <- predict(rf.model, cv, type = "prob")[, 2]
rf_probs_4 <- predict(rf.model, cv, type = "prob")[, 2]
rf_auc <- auc(cv$is_fraud, rf_probs)
confusionMatrix(cv$is_fraud, rf.predict)
rf_auc
```

Rose Sampled data RF:

```{r}
set.seed(10)
rf.model <- randomForest(is_fraud ~ ., data = rose_train_data,
                         ntree = 500, nodesize = 20)

rf.predict <- predict(rf.model, cv)
rf_probs <- predict(rf.model, cv, type = "prob")[, 2]
rf_probs_5 <- predict(rf.model, cv, type = "prob")[, 2]
rf_auc <- auc(cv$is_fraud, rf_probs)
confusionMatrix(cv$is_fraud, rf.predict)
rf_auc
```

ROC Plots Random Forest with Sampled Data:

```{r message=FALSE}
model_labels <- c("Normal", "Over Sampling" ,"Under Sampling", "Mixed Sampling", "Rose Sampling")

plot(0, 0, xlim = c(0, 1), ylim = c(0, 1), type = "n", xlab = "False Positive Rate", ylab = "True Positive Rate", main = "ROC Curves - Different Sampling Methods in Random Forest")

legend_labels <- c()
auc_values <- c()

for (i in 1:5) {
  pred_probs_model <- eval(parse(text = paste0("rf_probs_", i)))
  roc_obj <- roc(test_y, pred_probs_model)
  lines(roc_obj, col = i)
  auc_values[i] <- auc(roc_obj)
  legend_labels <- c(legend_labels, paste(model_labels[i], "AUC =", round(auc_values[i], 4)))
}

abline(v = seq(0, 1, 0.1), h = seq(0, 1, 0.1), col = "lightgray", lty = "dotted")

legend("bottomleft", legend = legend_labels, col = 1:5, lwd = 1)

```

XG Boost on Sampled Data:

```{r message=FALSE}

set.seed(565)

train_data_XG <- model.matrix(~.-1, data = train)

train_x <- train_data_XG[, -19]
train_y <- train_data_XG[, 19]

xgb_model0 <- xgboost(data = as.matrix(train_x),
                      label = train_y,
                      objective = "binary:logistic",
                      eval_metric = "auc",
                      nrounds = 100,
                      verbose = 0)



predictions_1 <- predict(xgb_model0, newdata = as.matrix(test_x))

roc_obj1 <- roc(test_y, predictions_1)

xg.auc <- auc(roc_obj1)
cat("AUC:", xg.auc, "\n")

```

```{r}
predicted_labels <- ifelse(predictions_1 >= 0.5, 1, 0)

xg.acc <- sum(predicted_labels == test_y) / length(test_y)
cat("Accuracy:", xg.acc, "\n")

confusion_matrix <- table(Actual = test_y, Predicted = predicted_labels)
print(confusion_matrix)

```

XG Boost Over:


```{r message=FALSE}

set.seed(56)

train_data_XG_over <- model.matrix(~.-1, data = oversampled_train_data)

train_x <- train_data_XG_over[, -19]
train_y <- train_data_XG_over[, 19]

xgb_model1 <- xgboost(data = as.matrix(train_x),
                      label = train_y,
                      objective = "binary:logistic",
                      eval_metric = "auc",
                      nrounds = 100,
                      verbose = 0)

predictions_2 <- predict(xgb_model1, newdata = as.matrix(test_x))

roc_obj2 <- roc(test_y, predictions_2)

xg.over.auc <- auc(roc_obj2)
cat("AUC:", xg.over.auc, "\n")

```

```{r}
predicted_labels <- ifelse(predictions_2 >= 0.5, 1, 0)

xg.over.acc <- sum(predicted_labels == test_y) / length(test_y)
cat("Accuracy:", xg.over.acc, "\n")

confusion_matrix <- table(Actual = test_y, Predicted = predicted_labels)
print(confusion_matrix)

```

XGboost Under Sample:

```{r}

train_data_XG_under <- model.matrix(~.-1, data = undersampled_train_data)

train_x <- train_data_XG_under[, -19]
train_y <- train_data_XG_under[, 19]

xgb_model2 <- xgboost(data = as.matrix(train_x),
                      label = train_y,
                      objective = "binary:logistic",
                      eval_metric = "auc",
                      nrounds = 100,
                      verbose = 0)

predictions_3 <- predict(xgb_model2, newdata = as.matrix(test_x))

roc_obj3 <- roc(test_y, predictions_3)

plot(roc_obj3, main = "ROC Curve")

xg.under.auc <- auc(roc_obj3)
cat("AUC:", xg.under.auc, "\n")

```

```{r}

predicted_labels <- ifelse(predictions_3 >= 0.5, 1, 0)

confusion_matrix <- table(Actual = test_y, Predicted = predicted_labels)
print(confusion_matrix)


```

```{r}
xg.under.acc <- sum(predicted_labels == test_y) / length(test_y)
cat("Accuracy:", xg.under.acc, "\n")
```


XGboost Mix:

```{r}
train_data_XG_mix <- model.matrix(~.-1, data = mix_sampled_train_data)

train_x <- train_data_XG_mix[, -19]
train_y <- train_data_XG_mix[, 19]

xgb_model3 <- xgboost(data = as.matrix(train_x),
                      label = train_y,
                      objective = "binary:logistic",
                      eval_metric = "auc",
                      nrounds = 100,
                      verbose = 0)

predictions_4 <- predict(xgb_model3, newdata = as.matrix(test_x))

roc_obj4 <- roc(test_y, predictions_4)

plot(roc_obj4, main = "ROC Curve")

xg.mix.auc <- auc(roc_obj4)
cat("AUC:", xg.mix.auc, "\n")

```

```{r}

predicted_labels <- ifelse(predictions_4 >= 0.5, 1, 0)

confusion_matrix <- table(Actual = test_y, Predicted = predicted_labels)
print(confusion_matrix)


```

```{r}
xg.mix.acc <- sum(predicted_labels == test_y) / length(test_y)
cat("Accuracy:", xg.mix.acc, "\n")
```

XGboost Rose:

```{r}
train_data_XG_rose <- model.matrix(~.-1, data = rose_train_data)

train_x <- train_data_XG_rose[, -19]
train_y <- train_data_XG_rose[, 19]

xgb_model4 <- xgboost(data = as.matrix(train_x),
                      label = train_y,
                      objective = "binary:logistic",
                      eval_metric = "auc",
                      nrounds = 100,
                      verbose = 0)

predictions_5 <- predict(xgb_model4, newdata = as.matrix(test_x))

roc_obj5 <- roc(test_y, predictions_5)

xg.rose.auc <- auc(roc_obj5)
cat("AUC:", xg.rose.auc, "\n")

```

```{r}
predicted_labels <- ifelse(predictions_5 >= 0.5, 1, 0)

confusion_matrix <- table(Actual = test_y, Predicted = predicted_labels)
print(confusion_matrix)


```

```{r}
xg.rose.acc <- sum(predicted_labels == test_y) / length(test_y)
cat("Accuracy:", xg.rose.acc, "\n")
```

```{r}
result.xg.auc <- data.frame(xg_normal_auc = xg.auc, xg_over_auc = xg.over.acc, xg_under_auc = xg.under.auc, xg_mix_auc = xg.mix.auc, xg_rose_auc = xg.rose.auc)
result.xg.auc

```

```{r}
result.auc
```

```{r}
names <- dimnames(data.matrix(train_data_XG_over[,-21]))[[2]]

importance_matrix <- xgb.importance(names, model = xgb_model1)

font_size <- 12
xgb.plot.importance(importance_matrix[1:15,])
```


ROC Plots XG Boosted:

```{r message=FALSE}
model_labels <- c("Normal", "Over Sampling" ,"Under Sampling", "Mixed Sampling", "Rose Sampling")

plot(0, 0, xlim = c(0, 1), ylim = c(0, 1), type = "n", xlab = "False Positive Rate", ylab = "True Positive Rate", main = "ROC Curves - XGBoost on Different Sampling Methods")

legend_labels <- c()
auc_values <- c()

for (i in 1:5) {
  pred_probs_model <- eval(parse(text = paste0("predictions_", i)))
  roc_obj <- roc(test_y, pred_probs_model)
  lines(roc_obj, col = i)
  auc_values[i] <- auc(roc_obj)
  legend_labels <- c(legend_labels, paste(model_labels[i], "AUC =", round(auc_values[i], 4)))
}

abline(v = seq(0, 1, 0.1), h = seq(0, 1, 0.1), col = "lightgray", lty = "dotted")

legend("bottomleft", legend = legend_labels, col = 1:5, lwd = 1)

```
